\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/intro.tex
editing for grammar

%\sean{Ben mentioned about discussing the limitations of list approach. Below is the paragraph from chi submission for your reference.}
%
\changes{Today, commercial solutions for controlling physical devices (such as Belkin WeMo) use smartphones as {\em universal remote controls} -- users first browse a list of all available devices and then call up a device-specific user interface. This method faces {\em naming} issues (where is ``Light 4 in Area E''?) and {\em scaling} issues as the number of controlled devices increases.}
%
%% previous approaches are limited
Past research has used direct aiming at target devices in space with phones to overcome these problems~\cite{beigl_point_1999,patel_2-way_2003}. Such techniques have a few drawbacks: the aiming device first has to be retrieved (e.g., from a pocket); user's hands have to be free for operation; and the user's visual attention is split between looking down at a screen and out at targets in the world.

>>>>

%\sean{Ben mentioned about discussing the limitations of list approach. Below is the paragraph from chi submission for your reference.}
%
\changes{Today, companies like Samsung and Whirlpool are making smart appliances with companion applications that use smartphones as {\em universal remote controls}. With these applications, the user can select a device from a list in order to control it with a device-specific user interface. This method faces {\em naming} issues (i.e. "what do we name the lamp on the left?") and {\em scaling} issues as the number of controlled devices increases. These solutions also present a necessarily flawed mapping from the positions of the appliances in the rich, 3-dimensional world to their place in a 1D or 2D list presented on the screen. }
%
%% previous approaches are limited
Past research has used direct aiming at target devices in space with phones to overcome these problems~\cite{beigl_point_1999,patel_2-way_2003}. Such techniques have a few drawbacks: the aiming device first has to be retrieved; the user's hands have to be free for operation; and the user's visual attention is split between looking down at a screen and out at targets in the world.
